### 2023-01-26 README.Rmd
Updates for submission
Updates

`clarify` implements simulation-based inference for computing functions of model parameters, such as average marginal effects. See the `clarify` [website](https://iqss.github.io/clarify) for documentation and other examples.

Simulation-based inference provides a compromise to these two methods: it is more accurate than the delta method because it does not require assumptions 2) and 3), and it is faster and more stable than bootstrapping because the model only needs to be fit once. Simulation-based inference involves simulating model coefficients from their multivariate distribution using their estimated values and covariance from a single model fit to the original data, computing the quantities of interest from each set of model coefficients, and then performing inference using the resulting distribution of the estimates as their sampling distribution. Confidence intervals can be computed using the percentiles of the resulting sampling distribution, and p-values can be computed by inverting the confidence intervals. Alternatively, if the resulting sampling distribution is normally distributed, its standard error can be estimated as the standard deviation of the estimates and normal-theory confidence intervals and p-values can be computed.

The `clarify` package was designed to provide a simple, general interface for simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

@@

Below is an example of performing g-computation for the ATT after logistic regression to compute the marginal log risk ratio and its confidence interval:

```{r example, fig.width=7, fig.height=3}
library(clarify)

@@

# Fit the model
fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married
                                   + nodegree + re74 + re75),
           data = lalonde, family = binomial)

# Simulate coefficients from a multivariate normal distribution
set.seed(123)
sim_coefs <- sim(fit)

# Apply a function that computes the g-computation estimate for the ATT
# to models with the estimated coefficients replaced by the simulated ones
sim_est <- sim_apply(sim_coefs, function(fit) {
  d <- subset(lalonde, treat == 1)
  d$treat <- 1
  p1 <- mean(predict(fit, newdata = d, type = "response"))
  d$treat <- 0
  p0 <- mean(predict(fit, newdata = d, type = "response"))
  c(`E[Y(0)]` = p0, `E[Y(1)]` = p1, `log(RR)` = log(p1 / p0))
}, verbose = FALSE)

@@

# View the estimates, confidence intervals, and p-values
summary(sim_est, null = c(NA, NA, 0))

@@

`clarify` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing. We can compute the log marginal risk ratio below:

```{r}
# Marginal risk ratio ATT, simulation-based
sim_est <- sim_ame(sim_coefs, var = "treat", subset = treat == 1,
                   contrast = "log(RR)", verbose = FALSE)

@@

summary(sim_est, null = c(NA, NA, 0))
```

We could have used `marginaleffects`, which uses the delta method instead:

```{r}
# Marginal risk ratio ATT, delta method-based
marginaleffects::comparisons(fit, variables = "treat",
                             newdata = subset(lalonde, treat == 1),
                             transform_pre = "lnratioavg") |>
  summary()
```

The plot of the simulated sampling distribution indicates that the sampling distribution for the log risk ratio is not normally distributed around the estimate, indicating that the delta method may be a poor approximation and the asymmetric confidence intervals produced using the simulation may be more valid.

If we want to compute the marginal risk ratio, we can do that using `transform()` on the already-produced output:

```{r}
#Transform estimates into new quantities of interest
sim_est <- transform(sim_est, `RR` = exp(`log(RR)`))
summary(sim_est, null = c(NA, NA, 0, 1))
```

@@

`clarify` offers parallel processing for all estimation functions to speed up computation.

The methodology of simulation-based inference is described in King, Tomz, and Wittenberg (2000).

>>>>

`clarify` implements simulation-based inference for computing functions of model parameters, such as average marginal effects and predictions at representative values of the predictors. See the `clarify` [website](https://iqss.github.io/clarify/) for documentation and other examples. `clarify` was designed to replicate and expand on functionality previously provided by the `Zelig` package.

@@

Below is an example of performing g-computation for the average treatment effect on the treated (ATT) after logistic regression to compute the marginal log risk ratio and its confidence interval. First we load the data (in this case the `lalonde` dataset from `MatchIt`) and fit a logistic regression using functions outside of `clarify`:

```{r, fig.width=7, fig.height=3}
library(clarify)

@@

# Fit the model
fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married +
                                     nodegree + re74 + re75),
           data = lalonde, family = binomial)
```

Next, to estimate the ATT risk ratio, we simulate coefficients from their implied distribution and compute the effects of interest in each simulation, yielding a distribution of estimates that was can summarize and use for inference:

```{r example, fig.width=7, fig.height=3}
# Simulate coefficients from a multivariate normal distribution
set.seed(123)
sim_coefs <- sim(fit)

# Marginal risk ratio ATT, simulation-based
sim_est <- sim_ame(sim_coefs, var = "treat", subset = treat == 1,
                   contrast = "RR", verbose = FALSE)

@@

# View the estimates, confidence intervals, and p-values
summary(sim_est, null = c(`RR` = 1))

@@

Below, we provide information on the framework `clarify` uses and some other examples. For a complete vignette, see `vignette("clarify")`.

Simulation-based inference provides a compromise to these two methods: it is more accurate than the delta method because it does not require assumptions 2) and 3), and it is faster and more stable than bootstrapping because the model only needs to be fit once. Simulation-based inference involves simulating model coefficients from their multivariate distribution using their estimated values and covariance from a single model fit to the original data, computing the quantities of interest from each set of model coefficients, and then performing inference using the resulting distribution of the estimates as their sampling distribution. Confidence intervals can be computed using the percentiles of the resulting sampling distribution, and p-values can be computed by inverting the confidence intervals. Alternatively, if the resulting sampling distribution is normally distributed, its standard error can be estimated as the standard deviation of the estimates and normal-theory confidence intervals and p-values can be computed. The methodology of simulation-based inference is explained in King, Tomz, and Wittenberg (2000).

`clarify` was designed to provide a simple, general interface for simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

In the example above, we used `sim_ame()` to compute the ATT, but we could have also done so manually using `sim_apply()`, as demonstrated below:

```{r example2, fig.width=7, fig.height=3}
# Write a function that computes the g-computation estimate for the ATT
ATT_fun <- function(fit) {
  d <- subset(lalonde, treat == 1)
  d$treat <- 1
  p1 <- mean(predict(fit, newdata = d, type = "response"))
  d$treat <- 0
  p0 <- mean(predict(fit, newdata = d, type = "response"))
  c(`E[Y(0)]` = p0, `E[Y(1)]` = p1, `RR` = p1 / p0)
}

# Apply that function to the simulated coefficient
sim_est <- sim_apply(sim_coefs, ATT_fun, verbose = FALSE)

@@

# View the estimates, confidence intervals, and p-values;
# they are the same as when using sim_ame() above
summary(sim_est, null = c(`RR` = 1))

The plot of the simulated sampling distribution indicates that the sampling distribution for the risk ratio is not normally distributed around the estimate, indicating that the delta method may be a poor approximation and the asymmetric confidence intervals produced using the simulation may be more valid.

If we want to compute the risk difference, we can do that using `transform()` on the already-produced output:

```{r}
#Transform estimates into new quantities of interest
sim_est <- transform(sim_est, `RD` = `E[Y(1)]` - `E[Y(0)]`)
summary(sim_est, null = c(`RR` = 1, `RD` = 0))
```

@@

See `vignette("Zelig", package = "clarify")` for more examples of translating a `Zelig`-based workflow into one that uses `clarify` to estimate the same quantities of interest.

`clarify` offers parallel processing for all estimation functions to speed up computation. Functionality is also available for the analysis of models fit to multiply imputed data. See `vignette("clarify")` for more details.

## References
